### 2023-04-12 definitions.tex
up

Given $(X,\leq)$ a quasi-ordering, an {\em upward-closed set} is any set $U \subseteq X$ such that if $y \geq x$ and $x \in U$ then $y \in U $.
A {\em downward-closed set} is any set $D \subseteq X$ such that if $y \leq x$ and $x \in D$ then $y \in D $. 
To any subset $A \subseteq X$, we may associate
its {\em upward-closure},
 $\uparrow A = \{x \in X \mid \exists a \in A ~ y \geq a\}$
 and its 
 {\em downward-closure},
 $\downarrow A = \{x \in X \mid \exists a \in A ~ y \leq a\}$. 
We abbreviate $\uparrow \{x\}$ (resp. $\downarrow \{x\}$)
as $\uparrow x$ (resp. $\downarrow x$).

@@

% \textcolor{red}{Define what an Ideal is. Actually an Ideal is just an upward-closed set, so maybe this just adds some confusion. Anti-ideal just downward closed so again just not that helpful a notation. Maybe have a }

\iffalse
\begin{definition}
A {\em bi-ideal} $I \subseteq S$ is an upward-closed and downward-closed set, i.e
$\uparrow I = I = \downarrow I$.
\end{definition}

"Bi-ideals often represent “control states” as in [cf \%]. "
% Parosh Aziz Abdulla, Karlis Cerans, Bengt Jonsson & Yih-Kuen Tsay (1996): General Decidability Theorems for Infinite-State Systems. In: Proc. LICS 1996, IEEE Computer Society Press, pp. 313–321,

% \textcolor{red}{Probably one can already 'deduce' from this that ideal $I$ and anti-ideal $J$ for resp. good and bad states, in the case of e.g. timed automata would be given by sets of states}
\fi

@@

>>>>

Given $(X,\leq)$ a quasi-ordering, an {\em upward-closed set} is any set $U \subseteq X$ such that if $y \geq x$ and $x \in U$ then $y \in U $.
A {\em downward-closed set} is any set $D \subseteq X$ such that if $y \leq x$ and $x \in D$ then $y \in D $. 
It is an {\em ideal } if it is also {\em directed}, i.e. it is nonempty and for every $a,b \in D$, there exists $c \in D$ such that $a \leq c$ and $b \leq c$.
To any subset $A \subseteq X$, we may associate
its {\em upward-closure},
 $\uparrow A = \{x \in X \mid \exists a \in A ~ y \geq a\}$
 and its 
 {\em downward-closure},
 $\downarrow A = \{x \in X \mid \exists a \in A ~ y \leq a\}$. 
We abbreviate $\uparrow \{x\}$ (resp. $\downarrow \{x\}$)
as $\uparrow x$ (resp. $\downarrow x$).

@@

@@

\begin{definition}{\cite{BFM-ic17}} 
A class $C$ of WSTS is {\em ideally effective} if
\begin{itemize}
\item the function mapping the encoding of a configuration $s$ of an ordered transition system
to the encoding of the ideal $\downarrow s$ is computable;
\item inclusion of ideals is decidable;
\item the downward closure $\downarrow \post(I)$ expressed as a finite union of ideals is com-
putable from the ideal $I$.
\end{itemize}
\end{definition}

\mathieu{I'm using the notion of ideally effective-ness for WBTS here}
